From Likes to Change: Assessing the Impact of Citizen Engagement on the European

### 2023-06-14 Article.Rmd
Cristina included as author

  Tanase Tasente (Orcid ID: https://orcid.org/0000-0002-3164-5894) is a lecturer and ERASMUS coordinator at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta. He holds a bachelor's, master's, and doctoral degree in Communication Sciences and a master's degree in European Administration, Institutions, and Public Policies. With over 100 published scientific papers and 4 authored books on institutional communication through social media and public policy strategies, the author has made significant contributions to the academic community. Additionally, he is the director of two international public relations companies, Plus Communication and International Communication & PR, where they have overseen marketing, advertising, and public relations campaigns for renowned multinational companies. His combination of academic and professional experience has equipped them with the necessary skills and knowledge to excel in various fields of communication and administration.
  Cristian Opariuc-Dan (Orcid ID: https://orcid.org/0000-0003-4079-0142) is a lecturer at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta. He holds a Bachelor's degree in Psychology, a Master's degree in Administrative Sciences, and a PhD in Psychology. He serves as the coordinator of the Law and Public Administration programs (part-time education) at Ovidius University and is an associate professor in the Doctoral Schools of Psychology and Education Sciences at the University of Bucharest and "Al. I. Cuza" University in Iasi. With over 50 scientific articles published in specialized journals and as the author and co-author of 5 books in the field of statistics and data analysis, he has demonstrated his expertise in the academic field.
abstract: |
  This study investigates the role of emotional resonance in social media  communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings  indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform. Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced  effect. Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues. An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse. The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others. This study lays the groundwork for refining communication strategies within a multi-platform   digital governance environment.

>>>>

    Tanase Tasente (Orcid ID: https://orcid.org/0000-0002-3164-5894) is a lecturer and ERASMUS coordinator at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta. He holds a bachelor's, master's, and doctoral degree in Communication Sciences and a master's degree in European Administration, Institutions, and Public Policies. With over 100 published scientific papers and 4 authored books on institutional communication through social media and public policy strategies, the author has made significant contributions to the academic community. Additionally, he is the director of two international public relations companies, Plus Communication and International Communication & PR, where they have overseen marketing, advertising, and public relations campaigns for renowned multinational companies. His combination of academic and professional experience has equipped them with the necessary skills and knowledge to excel in various fields of communication and administration.

    Cristian Opariuc-Dan (Orcid ID: https://orcid.org/0000-0003-4079-0142) is a lecturer at the Faculty of Law and Administrative Sciences at Ovidius University in Constanta. He holds a Bachelor's degree in Psychology, a Master's degree in Administrative Sciences, and a PhD in Psychology. He serves as the coordinator of the Law and Public Administration programs (part-time education) at Ovidius University and is an associate professor in the Doctoral Schools of Psychology and Education Sciences at the University of Bucharest and "Al. I. Cuza" University in Iasi. With over 50 scientific articles published in specialized journals and as the author and co-author of 5 books in the field of statistics and data analysis, he has demonstrated his expertise in the academic field.

    Cristina-Dana Popescu (Orcid ID: ) is a Lecturer at the Faculty of Letters, the Faculty of Law and Administrative Sciences and at the Faculty of Mathematics and Informatics at Ovidius University in Constanta. She holds a Bachelor’s degree in Philology at the University of Bucharest, the Faculty of Foreign Languages and Literatures, English and German Department, a Master's degree in Philosophy at the University “Al. I. Cuza”, Iaşi, Romania and a Ph.D. in Philology - British and American Literature, at the University “Al. I. Cuza”, Iaşi, Romania. She has been teaching English since 1999 being also a School Director for 12 years of a private High School in Constanta, she is an accomplished teacher with demonstrated ability to teach, motivate and direct students while maintaining high interest and achievement. She holds the Excellence Award within the Faculty of Letters, as the winner of the Performance in Education Competition at Ovidius University in Constanta. She also holds internationally recognized trainings in the field of psychology, being a licensed NLP Practitioner at the International Association for Neuro-Linguistic Programming and also a licensed of Silva Method, the Immersion Silva Life and Intuition System at Silva International Headquarters, Laredo, Texas, USA. She also holds the qualification of Trainer, COR Code 242401, certified by SC Training & Teaching Center, București.With over 30 scientific articles published in specialized journals at national and international conferences, author of ISI and BDI articles, participant both in CNCSIS grant teams and in University Projects as Expert in the Study Programs Pillars and Expert in Educational Material Development and also author of 3 books and co-author of 1 book in the field of literature and various specialized languages, she has demonstrated her expertise in the academic field.

abstract: |
  This study investigates the role of emotional resonance in social media  communications from the European Commission (EC) and its impact on public participation across various platforms including Facebook, Instagram, Twitter, and YouTube. Findings  indicate that emotionally resonant communications significantly enhance public engagement, with variations depending on the specific platform. Both positive and negative emotional resonance significantly impact participation, with the latter having a more pronounced  effect. Our research highlights the critical importance of platform-specific strategies and the incorporation of emotional resonance in public communications to foster participation in policy dialogues. An analysis of the engagement rates and sentiment across platforms reveals unique tonal variations in the EC's discourse. The effect of emotional resonance on public engagement is also found to be moderated by the choice of social media platform, with certain platforms more significantly moderating the relationship between emotional resonance and engagement than others. This study lays the groundwork for refining communication strategies within a multi-platform   digital governance environment.
